True versus apparent shapes of astrophysical bow shocks

### 2017-09-21 papers/Paper1/sec-conic.tex
Expand some fig captions and move figures between sections

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \begin{tabular}{@{}ll@{}}
    (a) & (b) \\
    \includegraphics{figs/projected-Rc-vs-i}
        & \includegraphics{figs/projected-R0-vs-i} \\
    (c) & (d) \\
    \includegraphics{figs/projected-R90-vs-i}
    & \includegraphics{figs/projected-R90-vs-Rc}
  \end{tabular}
  \caption[]{Effects of projection on quadrics of revolution:
    variation with inclination of characteristic radii. In panels
    (a)--(c), vertical rectangles show quartiles of \(|\sin i|\), which
    will be equally populated for an isotropic distribution of
    orientations. (a)~Projected radius of curvature, normalized by
    projected stand-off distance: \( \tilde{R}_c' = R'_c /
    R'_0\). (b)~Projected stand-off distance: \(R_0' / R_0\).
    (c)~Projected perpendicular radius, normalized by projected
    stand-off distance: \( \tilde{R}_{90}' = R'_{90} /
    R'_0\). (d)~Diagnostic diagram for dimensionless projected radii:
    \(\tilde{R}_{90}'\) versus \(\tilde{R}_c'\). }
  \label{fig:quadric-projection}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \begin{tabular}{@{}ll@{}}
    (a) & (b) \\
    \includegraphics{figs/projected-Rc-vs-i}
        & \includegraphics{figs/projected-R0-vs-i} \\
    (c) & (d) \\
    \includegraphics{figs/projected-R90-vs-i}
    & \includegraphics{figs/projected-R90-vs-Rc}
  \end{tabular}
  \caption[]{Effects of projection on quadrics of revolution:
    variation with inclination of characteristic radii.  Different
    line colors correspond to different quadric shapes (see key),
    while variation in line width corresponds to variation in the
    ``true'' dimensionless radius of curvature, \(\tilde{R}_c\), at
    the apex. Vertical gray rectangles show quartiles of \(|\sin i|\),
    which will be equally populated for an isotropic distribution of
    orientations. (a)~Projected radius of curvature, normalized by
    projected stand-off distance: \( \tilde{R}_c' = R'_c /
    R'_0\). (b)~Projected stand-off distance: \(R_0' / R_0\).
    (c)~Projected perpendicular radius, normalized by projected
    stand-off distance: \( \tilde{R}_{90}' = R'_{90} /
    R'_0\). (d)~Diagnostic diagram for dimensionless projected radii:
    \(\tilde{R}_{90}'\) versus \(\tilde{R}_c'\).  Shading indicates
    different classes of quadrics: hyperboloids (white), prolate
    spheroids (dark gray), and oblate spheroids (light gray), with the
    limiting case of paraboloids shown by the thin black line.}
  \label{fig:quadric-projection}
\end{figure*}

### 2017-09-21 papers/Paper1/sec-generic-model.tex
Include POS projection figure in section 3
And brief discussion in text
Correct errors in latex file
Remove repeated figure
Incorporated A' and q' results in  parabola appendix.
Restored projection section.
Correct errors and footnote
Create new figures. Move figure 8 to section 2.
- ~R'c vs inclination
- ~R'90 vs inclination
- T'c vs ~R'c
Expand some fig captions and move figures between sections

\section{Generic bow shock model}
\label{sec:generic-model}

\begin{figure}
% \includegraphics[width=\linewidth]{2winds-scheme}
\includegraphics[width=\linewidth]{figs/generic-bowshock}
\caption{Quasi-stationary bow shock structure formed by the
  interaction of two supersonic winds.  Lower-left inset box shows the
  case where the inner wind is anisotropic.   
  % the two winds problem. Any point in the shell is located with the
  % coordinates $(R,\theta)$, and $\theta_1$ is measured from the
  % external wind position
}
\label{fig:2-winds}
\end{figure}

@@

\subsection{Characteristic Radii}

In order to contrast different bow shock models, we  derive a set of measurable radii. Each model used should predict them and these predictions can be
compared with observations.

\begin{itemize}
\item Radius at axis of symmetry. Denoted as $R_0$. 
\item Radius of Curvature at the axis of symmetry. Denoted as $R_c$
\item Radius at the  perpendicular direction to the symmetry axis. Denoted as $R_{90}$
\item For open bow shocks, the asymptotic angle. Denoted as $\theta_\infty$
\end{itemize}

\begin{figure}
\includegraphics[width=\linewidth]{ch-radii_ed2}
\caption{Schematic representation of the characteristic radii $R_0$, $R_{90}$ and the radius of curvature at the symmetry axis $R_c$}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:

>>>>

\section{Generic two-wind bow shock model}
\label{sec:generic-model}

\begin{figure}
  % \includegraphics[width=\linewidth]{2winds-scheme}
  \includegraphics[width=\linewidth]{figs/generic-bowshock}
  \caption{Quasi-stationary bow shock structure formed by the
    interaction of two supersonic winds.  Lower-left inset box shows
    the case where the inner wind is anisotropic. The streamlines
    (thin lines) are drawn so as to be qualitatively realistic: they
    are straight in regions of hypersonic flow, but curved in subsonic
    regions, responding to pressure gradients in the shocked shells.}
\label{fig:2-winds}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/bowshock-crw-variables}
  \caption[]{Schematic diagram of two-wind interaction problem,
    following \citet{Canto:1996}.}
  \label{fig:crw-schema}
\end{figure}

@@

\subsection{Characteristic Radii}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/characteristic-radii}
  \caption{Characteristic radii in the body frame.}
  \label{fig:characteristic-radii}
\end{figure}

In order to contrast different bow shock models, we derive a set of
measurable radii. Each model used should predict them and these
predictions can be compared with observations.
\begin{itemize}
\item Radius at axis of symmetry. Denoted as $R_0$.
\item Radius of Curvature at the axis of symmetry. Denoted as $R_c$
\item Radius at the perpendicular direction to the symmetry
  axis. Denoted as $R_{90}$
\item For open bow shocks, the asymptotic angle. Denoted as
  $\theta_\infty$
\end{itemize}

% \begin{figure}
%   \includegraphics[width=\linewidth]{ch-radii_ed2}
%   \caption{Schematic representation of the characteristic radii
%   $R_0$, $R_{90}$ and the radius of curvature at the symmetry axis
%   $R_c$}
% \end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:
